\thetitle

### 2017-12-17 TeX/manuscript.tex

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace, fancyhdr, hyperref, xcolor, tikz}
\usepackage{subcaption}
\usepackage{float}
\usepackage{marginnote}

\usetikzlibrary{positioning, intersections, calc, arrows}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\newcommand{\comment}[1]{}

\newcommand{\thetitle}{Symbolic Manipulation and Computation in the Same Graph}

@@

\begin{abstract}

    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does. A fundamental difference between human neural network and current machine neural networks is that only human networks combine symbolic reasoning with computation. \\

@@

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace, fancyhdr, hyperref, xcolor, tikz, subcaption, float, marginnote}

\usetikzlibrary{positioning, intersections, calc, arrows}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\newcommand{\comment}[1]{}
\newcommand{\thetitle}{Symbolic Manipulation and Computation in the Same Graph}

@@

\begin{abstract}
    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does. A fundamental difference between human neural network and current machine neural networks is that only human networks combine symbolic reasoning with computation. \\

@@

 Figure \ref{fig:sig-neuron} illustrates a neuron that receives three ordered inputs.

 \begin{figure}[!htb]

 \centering
 \begin{tikzpicture}
